COG-ED Manuscript

### 2021-08-23 06_Paper/COG-ED/Manuscript.Rmd
removed a temporary variable
added part of the methods section

@@

  remove(ntlx)

>>>>

# Methods

We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.

##Revising the COG-ED paradigm
The thought process behind this revision is illustrated in Figure 1.
It shows how different modifications of the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back the most, 3-back less, and 1-back the least.
We adapted the COG-ED paradigm until it accurately reflected this preference, arriving at our version, the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
The COG-ED paradigm sets the SV of 1-back to 1, so regardless of the response pattern, the SV of 1-back does not change.
Adding an ED round comparing 2-back and 3-back shows more differentiation between the SVs those two levels, but leaves the SV of 1-back unchanged.
Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs still contain the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
Therefore, the solution and our final COG-ER-ED paradigm reduces the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each ED round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The n-back level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The n-back level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from each comparison in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV is still an absolute and a relative value, which allows the computation of an AUC and therefore a quantification of the participant's ED behaviour.

@@

  remove(ntlx, newdata)
